---
title: "625 Final Project README"
author: "JA, MK, JT"
date: "2023-12-10"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FinalProject625  



# Description
The goal of the package FinalProject625 is to run a federated learning analysis.  This is a way to generate a statistical summary while allowing for data privacy.  More specifically, separate servers can all send summary statistics up to a central server which can then compile the summary data mimicing a much larger analysis.  This package focuses on running a linear regression for  a health data set using insurance companies as the local servers. 


## Installation

You can install the development version of FinalProject625 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mich625/FinalProject625")
```

## Example

(note) We can write this once we have our final functions. I loaded in the dataset so we should be able to use that

```{r example}
library(hw3mklinreg)
mk_lm(Y = mtcars$mpg, X = cbind(mtcars$wt, mtcars$cyl), X_names = c("weight", "cylinders"))
```
